---
title: "Mariana Ozaeta's Resume"
author: Mariana Ozaeta
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set to true for a self-contained HTML page (slower to render)
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis',
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set to TRUE to turn links into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted, for placement at the end
links <- c()

source('parsing_functions.R')

# Read the data and keep only rows tagged for the resume
position_data <- read_csv('positions.csv') %>%
  filter(in_resume) %>%
  mutate(
    # Collapse the two position types into one printed section
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions',
      TRUE ~ section
    )
  )
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> Mozaeta12@gmail.com
- <i class="fa fa-github"></i> github.com/t00th-blip
- <i class="fa fa-map-marker"></i> Phoenix, AZ


Evaluation Methods {#skills}
--------------------------------------------------------------------------------

- Mixed-methods design
- Needs, process & outcome evaluation
- Logic models & evaluation plans
- Bilingual instrument development
- Semi-structured interviewing
- Qualitative coding
- Participatory & community-based methods
- Data equity principles
- IRB protocol development


Analysis & Tools {#tools}
--------------------------------------------------------------------------------

- R · RStudio · R Markdown
- Multiple regression; descriptive & correlation statistics
- Data cleaning & quality assurance
- Data visualization
- SurveyMonkey · Microsoft Office · SharePoint · Salesforce


Languages {#languages}
--------------------------------------------------------------------------------

- English — native
- Spanish — fluent, including instrument development and interviewing


More info {#more-info}
--------------------------------------------------------------------------------

Project case studies and code at
[github.com/t00th-blip/Portfolio](https://github.com/t00th-blip/Portfolio).


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with [**pagedown**](https://github.com/rstudio/pagedown).

Source: [github.com/t00th-blip/Resume](https://github.com/t00th-blip/Resume).

Last updated on `r Sys.Date()`.




Main
================================================================================

Mariana Ozaeta {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- "Mixed-methods program evaluator completing an M.S. in Program Evaluation and Data Analytics at Arizona State University (December 2026).

I carry evaluations end to end — logic model and IRB protocol through bilingual instrument design, quantitative and qualitative analysis, and findings translated into recommendations for boards and executive decision-makers. Equity-centered, participatory design is core training, not an overlay.

Case studies and code: [github.com/t00th-blip/Portfolio](https://github.com/t00th-blip/Portfolio)
"

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```



Evaluation & Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```



Projects {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('projects')
```
